Working document to try to explain why/how ATAs influence coexistence in an intuitive way for referee 3

### 2023-07-11 paper/ExplanationOfATAEffectsWorkingDoc.tex
starting on ecological explanation
this for now

>>>>

\section{Ecological explanation}
Under Modern Coexistence Theory, the outcome of coexistence is determined by niche differences and fitness differences (Chesson 2000, Adler 2007). When niche differences overcome fitness differences, coexistence is possible. Niche differences are driven by stabalizing mechanisms (such as the storage effect), which are defined as mechanisms that cause a species to limit itself more than it limits others, i.e., the species experiences more intraspecific competition than interspecific competition.
